|

### 2025-12-02 manuscript/pre_print.qmd
Leigh's edit to discussion and COIs

    affil-id: 6,2,7

@@

  Preprint, please cite as: Kirwan, R., Peele, L., Nuckols, G., Kohlhoff, G., Cabré, H., Olenick, A., and Steele, J. (2025). Resting energy expenditure of women with and without polycystic ovary syndrome: a systematic review and meta-analysis. medrχiv DOI: TO ADD. Address for correspondence: james@steele-research.com

@@

These findings challenge the widely held belief that PCOS is inherently associated with a slower metabolism [@@teedeRecommendations2023International2023], predisposing women with PCOS to weight gain. This belief may mistakenly lead to recommendations centred on slightly more severe calorie restriction to achieve weight-loss goals, compared with recommendations for the general population, as primary management strategies for women with PCOS [@ozgensaydamWeightManagementStrategies2021]. Recognising that there may be minimal differences in REE between women with PCOS and those without can inform both clinical and public practices, potentially leading to a shift in focus away from a requirement for more severe caloric restriction as a primary method of treatment towards more comprehensive, individualised, and psychologically safe approaches to care [@teedeRecommendations2023International2023].

@@

# Financial Disclosures/Conflicts of Interest
Hannah Cabré was supported by the National Institute of Diabetes and Digestive and Kidney Diseases of the National Institutes of Health under Award Number T32DK064584. James Steele provides research consultancy through his company Steele Research Limited, is contracted currently by MacroFactor and Kieser Australia through Steele Research Limited, and has also received travel expenses and honoraria for speaking from fit20 International, Exercise School Portugal, and Discover Strength.

The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health or any other funding agencies or institutions noted above.

>>>>

    affil-id: 2,6,7

@@

  Preprint, please cite as: Kirwan, R., Peele, L., Nuckols, G., Kohlhoff, G., Cabré, H., Olenick, A., and Steele, J. (2025). Resting energy expenditure of women with and without polycystic ovary syndrome: a systematic review and meta-analysis. medrxiv DOI: TO ADD. Address for correspondence: james@steele-research.com

@@

These findings challenge the widely held belief that PCOS is inherently associated with a slower metabolism [@@teedeRecommendations2023International2023], predisposing women with PCOS to weight gain. This belief largely stems from a single but influential 2009 study from Georgopoulos et al. that reported a significantly reduced BMR in women with PCOS [@georgopoulosBasalMetabolicRate2009], which has been widely cited and reinforced in both academic and clinical contexts. However, as we have noted, this study along with others [@kritikouA2BV3Adrenergic2006; @saltamavrosAlpha2Beta2007; @koikaAssociationPro12AlaPolymorphism2009] have numerous reporting errors which led us to drop them from our present analysis (though sensitivity analysis including them did not alter our overall conclusions). The mistaken belief that REE is lower for those with PCOS may have mistakenly lead to recommendations centred on slightly more severe calorie restriction to achieve weight-loss goals, compared with recommendations for the general population, as primary management strategies for women with PCOS [@ozgensaydamWeightManagementStrategies2021]. Recognising that there may be minimal differences in REE between women with PCOS and those without can inform both clinical and public practices, potentially leading to a shift in focus away from a requirement for more severe caloric restriction as a primary method of treatment towards more comprehensive, individualised, and psychologically safe approaches to care [@teedeRecommendations2023International2023].

@@

# Financial Disclosures/Conflicts of Interest
Greg Nuckols and Leigh Peele are employed by MacroFactor, a nutrition-tracking app. Hannah Cabré was supported by the National Institute of Diabetes and Digestive and Kidney Diseases of the National Institutes of Health under Award Number T32DK064584. Alyssa Olenick provides fitness coaching and scientific consulting under ALYSSA OLENICK LLC. She receives compensation from scientific consulting, speaking engagments, affiliated social media partnerships, and book publishing. James Steele provides research consultancy through his company Steele Research Limited, is contracted currently by MacroFactor and Kieser Australia through Steele Research Limited, and has also received travel expenses and honoraria for speaking from fit20 International, Exercise School Portugal, and Discover Strength.

The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health or any other funding agencies or institutions noted above. The authors declare no other conflicts of interest related to the submitted work
